Change point analysis

### 2023-08-24 stats/gazemodel.Rmd
adjust analysis and plots

# careful, this takes a while... 
model_kids <- readRDS("../data/gazemodel_kids.rds")
model_kids_dev_prior <- readRDS("../data/gazemodel_kids_dev_prior.rds")
```

@@

inf_samp_devp <- model_kids_dev_prior%>%
  filter(scope == "global", 
         parameter == "inference", 
         type != "sigma") %>%
  pivot_wider(names_from = "type", values_from = "value") %>%
  sample_n(1000) %>%
  expand_grid(age = seq(0, 3, 0.1)) %>%
  mutate(sd = exp(intercept + slope * age))

id_devp <- model_kids_dev_prior%>%
  filter(scope == "id", 
         type == "sd") %>%
  group_by(id) %>%
  summarise(mode = estimate_mode(value),
            lci = hdi_lower(value), 
            uci = hdi_upper(value)) %>%
  left_join(tango_kids %>% 
              select(subj_id, age, age_group) %>% 
              rename(id = subj_id) %>% 
              distinct(id, .keep_all = T)) %>%
  ungroup()

dev_plot <- ggplot() +
  geom_point(data = id_devp, aes(x = age, y = mode), alpha = 0.75, color = "darkgrey") +
  geom_line(data = inf_samp_devp, aes(x = age + 3, y = sd, group = paste(chain,iteration)), col = "blue", alpha = .01) +
  geom_line(data = inf_map_devp, aes(x = age+3, y = sd), col = "black", linewidth = 1.25) +
  scale_x_continuous(limits = c(3, 6), breaks = seq(3, 6, 0.5)) + 
  scale_y_continuous(limits = c(0, 6), breaks = seq(0, 6, 0.25)) +
  coord_cartesian(ylim = c(0, 3)) +
  labs(x = "Age", y = "Model parameter")

dev_plot
saveRDS(dev_plot, file = "../saves/gazemodel_dev_plot.rds")

@@

model_vs_data_plot <- ggplot(comparison_model_data_devp, aes(x = model_mode, y = data_mean)) +
  geom_point(aes(col = age)) +
  stat_cor(method = "pearson", label.x = 0.05, label.y = 4.9, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") +
  geom_smooth(method = "lm", col = "darkgrey", alpha = 0.25) +
  scale_color_viridis_c(direction = -1, alpha = 0.9, limits = c(3, 6), breaks = seq(3, 6, 0.5)) +
  labs(x = "Model parameter", y = "Data imprecision", color = "Age") + 
  scale_x_continuous(limits = c(0, 2.1), breaks = seq(0, 2, 0.5)) + 
  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1))

model_vs_data_plot
saveRDS(model_vs_data_plot, file = "../saves/gazemodel_model_vs_data.rds")
# ggsave("../figures/gazemodel_model_vs_data.png", width = 8, height = 5, scale = 1, bg = "white")
# ggsave("../figures/gazemodel_model_vs_data.pdf", width = 8, height = 5, scale = 1, bg = "white")
```

@@

```{r modelpred_gaze_plot}
# correlation model predicted imprecision vs data imprecision across target positions
modelpred_gaze_plot <- modelpred_gaze %>% 
  ggplot(., aes(x = model_mean, y = data_mean)) +
  geom_point(aes(col = targetBin)) +
  stat_cor(method = "pearson", label.x = 0.2, label.y = 4.9, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") +
  geom_abline(intercept = 0, slope = 1, linetype = 3) +
  scale_color_brewer(palette="BrBG") +
  labs(x = "Gaze model predicted imprecision", y = "Data imprecision", color = "Target bin") + 
  scale_x_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1)) + 
  scale_y_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1))

@@

saveRDS(modelpred_center, file = "../saves/gazemodel_modelpred_center.rds")

@@

# corr plot
modelpred_center_plot <- modelpred_center %>% 
  ggplot(., aes(x = model_mean, y = data_mean)) +
  geom_point(aes(col = targetBin), size = 0.8) +
  stat_cor(method = "pearson", label.x = 0.2, label.y = 4.9, aes(label = paste(..r.label..)), size = 3, r.accuracy = 0.01, cor.coef.name = "r") +
  geom_abline(intercept = 0, slope = 1, linetype = 3) +
  scale_color_brewer(palette="BrBG") +
  labs(x = "Model predicted imprecision", y = "Data imprecision", color = "Target bin") + 
  scale_x_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1)) + 
  scale_y_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1))

@@

saveRDS(modelpred_random, file = "../saves/gazemodel_modelpred_random.rds")

@@

# corr plot
modelpred_random_plot <- modelpred_random %>% 
  ggplot(., aes(x = model_mean, y = data_mean)) +
  geom_point(aes(col = targetBin), size = 0.8) +
  stat_cor(method = "pearson", label.x = 0.2, label.y = 4.9, aes(label = paste(..r.label..)), size = 3, r.accuracy = 0.01, cor.coef.name = "r") +
  geom_abline(intercept = 0, slope = 1, linetype = 3) +
  scale_color_brewer(palette="BrBG") +
  labs(x = "Model predicted imprecision", y = "Data imprecision", color = "Target bin") + 
  scale_x_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1)) + 
  scale_y_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1))

@@

  ggarrange(
    modelpred_center_plot + 
      labs(x = "Center bias model", y = "") +
      theme(legend.position = "none", 
            axis.text = element_text(size = 6), 
            axis.title = element_text(size = 8), 
            plot.subtitle = element_text(size = 8), 
            plot.margin = margin(0.2, 0.2, 0.2, 0, "cm")),

    modelpred_random_plot + 
      labs(x = "Random guessing model", y = "") +
      theme(legend.position = "none", 
            axis.text = element_text(size = 6), 
            axis.title = element_text(size = 8), 
            plot.subtitle = element_text(size = 8), 
            plot.margin = margin(0.2, 0.2, 0.2, 0, "cm")), 
    nrow = 2
  ),

@@

  ncol = 4, 
  nrow = 2, 
  widths = c(9, 11, 1, 11), 
  labels = c("A", "B", "", "C", "D", "E", "", "F")
)

gazemodel_plot
saveRDS(gazemodel_plot, "../saves/gazemodel_plot.rds")
ggsave("../figures/gazemodel_plot.png", width = 10, height = 5, scale = 1.4, bg = "white")
ggsave("../figures/gazemodel_plot.pdf", width = 10, height = 5, scale = 1.4, bg = "white")
```

@@

# Model comparison BayesFactor
## TODO GET DATA FROM SERVER
```{r read_data_mcomparison}
# devp_model_comp <- rbindlist(
#   list(
#        fread("../models/output/child_gaze_model_dev_prior_hedge_model_comparison_chain7.csv")%>%
#   group_by(chain, iteration, model)%>%
#   summarise(like = sum(loglike)),
#        fread("../models/output/child_gaze_model_dev_prior_hedge_model_comparison_chain8.csv")%>%
#   group_by(chain, iteration, model)%>%
#   summarise(like = sum(loglike)),
#        fread("../models/output/child_gaze_model_dev_prior_hedge_model_comparison_chain9.csv")%>%
#   group_by(chain, iteration, model)%>%
#   summarise(like = sum(loglike)),
#        fread("../models/output/child_gaze_model_dev_prior_hedge_model_comparison_chain10.csv")%>%
#   group_by(chain, iteration, model)%>%
#   summarise(like = sum(loglike)),
#        fread("../models/output/child_gaze_model_dev_prior_hedge_model_comparison_chain11.csv")%>%
#   group_by(chain, iteration, model)%>%
#   summarise(like = sum(loglike)),
#        fread("../models/output/child_gaze_model_dev_prior_hedge_model_comparison_chain12.csv")%>%
#   group_by(chain, iteration, model)%>%
#   summarise(like = sum(loglike))
#     ), use.names=TRUE)
```

```{r modelcomparison}
devp_model_comp %>%
  group_by(model,chain) %>%
  summarise(margllh = logSumExp(like)) %>%
  pivot_wider(names_from = model, values_from = margllh)

devp_model_comp %>%
  group_by(model) %>%
  summarise(margllh = logSumExp(like)) %>%
  pivot_wider(names_from = model, values_from = margllh) %>%
  summarise(bf_inf_center = inf - center, 
            bf_inf_guess = inf - guess)

devp_model_comp%>%
  ggplot(aes(x = like))+
  geom_histogram(alpha = .5, aes(fill = model), col = "black")+
  scale_fill_colorblind()+
  xlim(-8000, -5000)+
  theme_bw()
```

>>>>

# careful, this takes a while... 
model_kids <- readRDS("../data/gazemodel-kids.rds")
model_kids_dev_prior <- readRDS("../data/gazemodel-kids-dev-prior.rds")
```

@@

inf_samp_devp <- model_kids_dev_prior %>%
  filter(scope == "global", 
         parameter == "inference", 
         type != "sigma") %>%
  pivot_wider(names_from = "type", values_from = "value") %>%
  sample_n(1000) %>%
  expand_grid(age = seq(0, 3, 0.1)) %>%
  mutate(sd = exp(intercept + slope * age))

id_devp <- model_kids_dev_prior %>%
  filter(scope == "id", 
         type == "sd") %>%
  group_by(id) %>%
  summarise(mode = estimate_mode(value),
            lci = hdi_lower(value), 
            uci = hdi_upper(value)) %>%
  left_join(tango_kids %>% 
              select(subj_id, age, age_group) %>% 
              rename(id = subj_id) %>% 
              distinct(id, .keep_all = T)) %>%
  ungroup()

dev_plot <- ggplot() +
  geom_point(data = id_devp, aes(x = age, y = mode), alpha = 0.75, color = "darkgrey") +
  geom_line(data = inf_samp_devp, aes(x = age + 3, y = sd, group = paste(chain,iteration)), col = "blue", alpha = .01) +
  geom_line(data = inf_map_devp, aes(x = age + 3, y = sd), col = "black", linewidth = 1.25) +
  scale_x_continuous(limits = c(3, 6), breaks = seq(3, 6, 0.5)) + 
  scale_y_continuous(limits = c(0, 6), breaks = seq(0, 6, 0.25)) +
  coord_cartesian(ylim = c(0, 3)) +
  labs(x = "Age in years", y = expression(paste("Mode model parameter (", italic("\U03C3"[v]), ")")))

saveRDS(dev_plot, file = "../saves/gazemodel_dev_plot.rds")

@@

model_vs_data_plot <- ggplot(comparison_model_data_devp, aes(x = model_mode, y = data_mean)) +
  geom_point(aes(col = age)) +
  stat_cor(method = "pearson", label.x = 0.05, label.y = 4.9, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") +
  geom_smooth(method = "lm", col = "darkgrey", alpha = 0.25) +
  scale_color_viridis_c(direction = -1, alpha = 0.9, limits = c(3, 6), breaks = seq(3, 6, 0.5)) +
  labs(x = expression(paste("Mode model parameter (", italic("\U03C3"[v]), ")")), y = "Mean data imprecision", color = "Age") + 
  scale_x_continuous(limits = c(0, 2.1), breaks = seq(0, 2, 0.5)) + 
  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1))

model_vs_data_plot
saveRDS(model_vs_data_plot, file = "../saves/gazemodel_model_vs_data.rds")

# ggsave("../figures/gazemodel_model_vs_data.png", width = 8, height = 5, scale = 1, bg = "white")
# ggsave("../figures/gazemodel_model_vs_data.pdf", width = 8, height = 5, scale = 1, bg = "white")
```

@@

```{r modelpred_gaze_plot}
# correlation model predicted imprecision vs data imprecision across target positions
modelpred_gaze_plot <- modelpred_gaze %>% 
  ggplot(., aes(x = model_mean, y = data_mean)) +
  geom_point(aes(col = targetBin)) +
  stat_cor(method = "pearson", label.x = 0.2, label.y = 4.9, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") +
  geom_abline(intercept = 0, slope = 1, linetype = 3) +
  scale_color_brewer(palette="BrBG") +
  labs(x = "Mean predicted imprecision", y = "Mean data imprecision", color = "Target bin") + 
  scale_x_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1)) + 
  scale_y_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1))

@@

saveRDS(modelpred_center, file = "../saves/gazemodel_modelpred_center.rds")
modelpred_center <- readRDS(file = "../saves/gazemodel_modelpred_center.rds")

@@

# corr plot
modelpred_center_plot <- modelpred_center %>% 
  ggplot(., aes(x = model_mean, y = data_mean)) +
  geom_point(aes(col = targetBin), size = 0.8) +
  stat_cor(method = "pearson", label.x = 0.2, label.y = 4.9, aes(label = paste(..r.label..)), size = 3, r.accuracy = 0.01, cor.coef.name = "r") +
  geom_abline(intercept = 0, slope = 1, linetype = 3) +
  scale_color_brewer(palette="BrBG") +
  labs(x = "Mean predicted imprecision", y = "Mean data imprecision", color = "Target bin") + 
  scale_x_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1)) + 
  scale_y_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1))

@@

saveRDS(modelpred_random, file = "../saves/gazemodel_modelpred_random.rds")
modelpred_random <- readRDS(file = "../saves/gazemodel_modelpred_random.rds")

@@

# corr plot
modelpred_random_plot <- modelpred_random %>% 
  ggplot(., aes(x = model_mean, y = data_mean)) +
  geom_point(aes(col = targetBin), size = 0.8) +
  stat_cor(method = "pearson", label.x = 0.2, label.y = 4.9, aes(label = paste(..r.label..)), size = 3, r.accuracy = 0.01, cor.coef.name = "r") +
  geom_abline(intercept = 0, slope = 1, linetype = 3) +
  scale_color_brewer(palette="BrBG") +
  labs(x = "Mean predicted imprecision", y = "Mean data imprecision", color = "Target bin") + 
  scale_x_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1)) + 
  scale_y_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1))

@@

  ggarrange(
    modelpred_center_plot + 
      labs(title = "Center bias model", x = "", y = "") +
      theme(legend.position = "none", 
            axis.text = element_text(size = 6), 
            plot.title = element_text(size = 8), 
            plot.subtitle = element_text(size = 8), 
            plot.margin = margin(0.2, 0.2, 0.2, 0, "cm")),

    modelpred_random_plot + 
      labs(title = "Random guessing model", x = "", y = "") +
      theme(legend.position = "none", 
            axis.text = element_text(size = 6), 
            plot.title = element_text(size = 8), 
            plot.subtitle = element_text(size = 8), 
            plot.margin = margin(0.2, 0.2, 0.2, 0, "cm")), 
    nrow = 2
  ),

@@

  ncol = 4, 
  nrow = 2, 
  widths = c(9, 11, 1, 12), 
  labels = c("A", "B", "", "C", "D", "E", "", "F")
)

gazemodel_plot
saveRDS(gazemodel_plot, "../saves/gazemodel_plot.rds")
ggsave("../figures/gazemodel_plot.png", width = 10, height = 5, scale = 1.4, bg = "white")
ggsave("../figures/gazemodel_plot.pdf", width = 10, height = 5, scale = 1.4, bg = "white", device = cairo_pdf) 
# add cairo_pdf to enable greek symbols in pdf saving
```

@@

# Model comparison BayesFactor

```{r read_data_mcomparison}
modelcomparison_kids_bf <- readRDS("../data/gazemodel-kids-comparison-bf.rds")
modelcomparison_kids_samples <- readRDS("../data/gazemodel-kids-comparison-samples.rds")
```
```{r mcomparison}
# same as reading in modelcomparison_kids_bf
modelcomparison_kids_samples %>%
  group_by(model) %>%
  summarise(margllh = logSumExp(like)) %>%
  pivot_wider(names_from = model, values_from = margllh) %>%
  summarise(bf_inf_center = inf - center, 
            bf_inf_guess = inf - guess)
```

### 2023-08-24 stats/lifespan.Rmd
adjust analysis and plots

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) # data handling etc.
library(tidybayes) # for stat_halfeye, add_predictive_draws
library(tidyboot) # for bootstrapped CIs
library(brms) # modeling
library(cmdstanr) # modeling
library(Rbeast) # Bayesian change point analysis
library(janitor) # clean_names
library(ggpubr) # ggarrange

@@

  # raw data points
  geom_jitter(data = mdata, aes(x = age, y = mean_imprecision), alpha = 0.5, color = "darkgrey") +

@@

  # change points from beast
  geom_vline(xintercept = cps$cp, linetype = "dashed", alpha = 0.9, size = 0.75) +

  scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 5)) +
  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) + 
  labs(x = "Age in years", y = "Average imprecision in target width")

lifespan_plot

saveRDS(lifespan_plot, "../saves/lifespan_plot.rds")

ggsave("../figures/lifespan_all.png", width = 7, height = 4)
ggsave("../figures/lifespan_all.pdf", width = 7, height = 4)
```

```{r zoomed_plot}
# https://cran.r-project.org/web/packages/tidybayes/vignettes/tidy-brms.html
lifespan_plot_zoom <- mdata %>%
  add_epred_draws(mgaussianprocess, ndraws = 100) %>%
  ggplot(aes(x = age, y = mean_imprecision)) +

  # raw data points
  geom_jitter(data = mdata, aes(x = age, y = mean_imprecision), alpha = 0.5, color = "darkgrey") +

  # change points from beast
  geom_vline(xintercept = cps$cp, linetype = "dashed", alpha = 0.9, size = 0.75) +

  coord_cartesian(xlim = c(3, 10)) +
  scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 0.5)) +

  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) + 
  labs(x = "Age in years", y = "Average imprecision in target width")

lifespan_plot_zoom

saveRDS(lifespan_plot_zoom, "../saves/lifespan_plot_zoom.rds")

# ggsave("../figures/lifespan_zoom.png", width = 7, height = 4)
# ggsave("../figures/lifespan_zoom.pdf", width = 7, height = 4)
```

```{r arrange_plot}
arranged <- ggarrange(
  lifespan_plot, 
  lifespan_plot_zoom, 
  widths = c(2, 1.5), 
  labels = c("A", "B")
)

arranged

ggsave("../figures/lifespan_plot.png", width = 10, height = 3, scale = 1.2)
ggsave("../figures/lifespan_plot.pdf", width = 10, height = 3, scale = 1.2)
```

```{r try_ggbreak}
library(ggbreak)

lifespan_cut <- mdata %>%
  add_epred_draws(mgaussianprocess, ndraws = 100) %>%
  ggplot(aes(x = age, y = mean_imprecision)) +

  # raw data points
  geom_jitter(data = mdata, aes(x = age, y = mean_imprecision), alpha = 0.5, color = "darkgrey") +

  scale_x_cut(breaks = c(18), scales = "free", space = 0.001) +

  # model predictions spaghetti lines
  geom_line(aes(y = .epred, group=.draw), alpha = .075, color = "blue") +
  # mean model prediction
  stat_lineribbon(aes(y = .epred), .width = 0, color = "black", show.legend = F) +

  # change points from beast
  geom_vline(xintercept = cps$cp, linetype = "dashed", alpha = 0.9, size = 0.75) +

  scale_x_continuous(limits = c(3, 80), breaks = c(3:17, 20, 30, 40, 50, 60, 70, 80)) +
  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) +

  labs(x = "Age", y = "Mean imprecision", xdist = "", ydist = "")

lifespan_cut
```

```{r try_ggh4x}
library(ggh4x)

mdata %>%
  mutate(my_facet = age > 20.00) %>% 
  add_epred_draws(mgaussianprocess, ndraws = 100) %>%

  ggplot(aes(x = age, y = mean_imprecision)) +

    # raw data points
  geom_jitter(data = mdata, aes(x = age, y = mean_imprecision), alpha = 0.5, color = "darkgrey") +

    # model predictions spaghetti lines
  geom_line(aes(y = .epred, group=.draw), alpha = .075, color = "blue") +
  # mean model prediction
  stat_lineribbon(aes(y = .epred), .width = 0, color = "black", show.legend = F) +

  # for gap in x axis
  facet_grid(~ my_facet, scales = "free_x") +
  theme(strip.text.x = element_blank()) +

  ggh4x::facetted_pos_scales(x = list(
    my_facet == FALSE ~ scale_x_continuous(limits = c(3, 20), breaks = seq(3, 19, 1)),
    my_facet == TRUE ~ scale_x_continuous(limits = c(20, 80), breaks = seq(20, 80, 10))
)) +

  geom_vline(data = data.frame(xint=cps$cp[1:4], my_facet = FALSE), aes(xintercept = xint), linetype = "dotted") +
  geom_vline(data = data.frame(xint=cps$cp[5:6], my_facet = TRUE), aes(xintercept = xint), linetype = "dotted") +

  labs(x = "Age in years", y = "Average imprecision in target width") +

  # get rid of space between facets
  theme(panel.spacing = unit(0.1, "lines"))
```

>>>>

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) # data handling etc.
library(tidybayes) # for stat_halfeye, add_predictive_draws
library(tidyboot) # for bootstrapped CIs
library(brms) # modeling
library(cmdstanr) # modeling
library(Rbeast) # Bayesian change point analysis
library(janitor) # clean_names
library(ggpubr) # ggarrange
library(ggmagnify) # for plot inset

@@

  # raw data points
  geom_jitter(data = mdata, aes(x = age, y = mean_imprecision), alpha = 0.5, color = "darkgrey", size = 0.75) +

@@

  # change points from beast
  geom_vline(xintercept = cps$cp, linetype = "dashed", alpha = 0.9, size = 0.5) +

  # scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 5)) +
  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) + 
  labs(x = "Age in years", y = "Average imprecision in target width")

lifespan_plot
```

```{r magnify}
lifespan_combined <- lifespan_plot +
  scale_x_continuous(breaks = seq(0, 10, 1)) +
  coord_cartesian(clip = "off") + 
  theme(plot.margin = margin(t = 40, r = 60, l = 10, b = 10)) +

  # xmin, xmax, ymin, ymax
  geom_magnify(aes(from = age < 10), to = c(55, 90, 2.5, 4.5), axes = "xy", linewidth = 0.5, proj.linetype = 3, proj = "single") +

  scale_x_continuous(breaks = seq(0, 80, 5))

lifespan_combined

saveRDS(lifespan_combined, "../saves/lifespan_plot.rds")
ggsave("../figures/lifespan_plot.png", width = 7, height = 4)
ggsave("../figures/lifespan_plot.pdf", width = 7, height = 4)
```

### 2023-08-24 stats/magnet.Rmd
adjust analysis and plots

magnet_data %>% 
  ggplot(., aes(x = magnet_mean, y = tango_mean)) + 
  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
  geom_smooth(method = "lm", size = 1, alpha = 0.25, col = "darkgrey") +
  geom_point(color = "#005555") +
  stat_cor(method = "pearson", label.x = 3.5, label.y = 3.25, aes(label = paste(..r.label..)), size = 5, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(limits = c(0, 3.75), breaks = seq(0, 4, 0.5)) +
  scale_y_continuous(limits = c(0, 3.75), breaks = seq(0, 4, 0.5)) +
  labs(x = "Magnet mean", y = "Tango mean")
```

>>>>

magnet_data %>% 
  ggplot(., aes(x = magnet_mean, y = tango_mean)) + 
  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
  geom_smooth(method = "lm", size = 1, alpha = 0.25, col = "darkgrey") +
  geom_point(color = "#005555") +
  stat_cor(method = "pearson", label.x = 3.5, label.y = 3.25, aes(label = paste(..r.label..)), size = 5, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(limits = c(0, 3.75), breaks = seq(0, 4, 0.5)) +
  scale_y_continuous(limits = c(0, 3.75), breaks = seq(0, 4, 0.5)) +
  labs(x = "Magnet mean", y = "Tango mean")

magnet_data %>% 
  group_by(subj_id) %>% 
  mutate(tom_other = sum(desires, knowledge, content, explicit)) %>% 
  ggplot(., aes(x = tom_other, y = perspective_aggregate)) + 
  geom_smooth(method = "lm", size = 1, alpha = 0.25, col = "darkgrey") +
  geom_jitter(color = "#005555", width = 0.05, height = 0.05) +
  stat_cor(method = "pearson", label.x = 0, label.y = 1.1, aes(label = paste(..r.label..)), size = 5, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(limits = c(0, 4), breaks = seq(0, 4, 1)) +
  scale_y_continuous(limits = c(0, 2), breaks = seq(0, 2, 1)) +
  labs(x = "ToM excl. perspective-taking", y = "Perspective-taking")
```

### 2023-08-24 stats/supplements_changepoint_parameters.Rmd
adjust analysis and plots

```{r}
b11

plot(b11)

str(b11)

# Y: a vector of length N; the estimated trend component.It is the Bayesian model averaging of all the individual sampled trend.
b11$trend$Y

plot(b11, vars = c('t', 'y'))

plot(b11$time, b11$trend$Y, type = 'l') # #directly plot output: the fitted trend

plot(b11$time, b11$trend$cpOccPr) # #directly plot output: trend chgpt occurrence prob
```

```{r}
est <- tibble(age = x, data = y, model = b11$trend$Y)
cps <- b11$trend$cp[1:b11$trend$ncp_median]

ggplot(data = est, aes(data, model)) + 
  geom_point() +
  geom_smooth(method = "lm") + 
  stat_cor() +
  scale_x_continuous(limits = c(0, 3), breaks = seq(0, 3, 0.5)) +
  scale_y_continuous(limits = c(0, 3), breaks = seq(0, 3, 0.5))

n_distinct(est$model)

est %>% 
  pivot_longer(cols = c(data, model), names_to = "source") %>% 
  ggplot(aes(x = age, y = value, color = as.factor(source))) + 
  geom_point(alpha = 0.5) +
  geom_vline(xintercept = cps, linetype = "dashed", alpha = 0.9, size = 0.75) +
  scale_color_manual(values = c("darkblue", "orange")) +
  scale_x_continuous(limits = c(3, 80), breaks = seq(0, 80, 5)) +
  scale_y_continuous(limits = c(0, 2.5), breaks = seq(0, 2.5, 0.5)) + 
  labs(x = "Age", y = "Mean imprecision", color = "Source")

est %>% 
  pivot_longer(cols = c(data, model), names_to = "source") %>% 
  filter(source == "model", age >= 20) %>%
  ggplot(aes(x = age, y = value)) + 
  geom_point() +
  geom_vline(xintercept = cps, linetype = "dashed", alpha = 0.9, size = 0.75) +
  scale_x_continuous(limits = c(20, 80), breaks = seq(0, 80, 5)) +
  scale_y_continuous(limits = c(0.5, 1), breaks = seq(0.5, 1, 0.5)) +
  labs(x = "Age", y = "Mean imprecision")
```

>>>>

```{r luke}
library(tidyverse)
library(Rbeast) # Bayesian change point analysis
set.seed(42)

lifespan_data <- readRDS("../data/tango-lifespan.rds")

mdata <- lifespan_data %>% 
  group_by(subj_id, age, age_centered) %>% 
  summarize(mean_imprecision = mean(click_dist_balloons, na.rm = TRUE))

x <- mdata %>% arrange(age) %>% pull(age)
y <- mdata %>% arrange(age) %>% pull(mean_imprecision)

ibeast <- beast.irreg(y = y, time = x, season = "none", 
            torder.minmax = c(0, 0),
            tcp.minmax = c(0, 72), # as max nr, since 719 datapoints, 10 tseg.min
            tseg.min = 10, 
            mcmc.chains = 4, mcmc.burnin = 1000,  mcmc.samples = 10000, mcmc.seed = 42, 
            ci = TRUE)

# Y: a vector of length N; the estimated trend component.It is the Bayesian model averaging of all the individual sampled trend.
ibeast$trend$Y

# plotting with Rbeast plot function
plot(ibeast)

plot(ibeast, vars = c('t', 'y')) # plot time vs predicted values
plot(ibeast$time, ibeast$trend$Y, type = 'l') # directly plot output: the fitted trend line
plot(ibeast$time, ibeast$trend$cpOccPr) # directly plot output: trend chgpt occurrence prob

# create imprecision as observed in data and as predicted by cp analysis
est <- tibble(age = x, data = y, model = ibeast$trend$Y)
cps <- ibeast$trend$cp[1:ibeast$trend$ncp_median]

# check how many distinct fitted values
# => here question: 
# I'd assume that we need as many distinct
n_distinct(est$model)

# plot raw data and fitted values from cp analysis
est %>% 
  pivot_longer(cols = c(data, model), names_to = "source") %>% 
  ggplot(aes(x = age, y = value, color = as.factor(source))) + 
  geom_point(alpha = 0.5) +
  geom_vline(xintercept = cps, linetype = "dashed", alpha = 0.9, size = 0.75) +
  scale_color_manual(values = c("darkblue", "orange")) +
  scale_x_continuous(limits = c(3, 80), breaks = seq(0, 80, 5)) +
  scale_y_continuous(limits = c(0, 2.5), breaks = seq(0, 2.5, 0.5)) + 
  labs(x = "Age", y = "Mean imprecision", color = "Source")
```
